Re-fit

### 2023-01-14 scripts/r/04_refit/refit_jvc.Rmd
🐛 - fix error due to unzipped folder
🐛 - let code run; remove obsolete code

@@

if(F) {
msa_raw <- tibble(
  path = Sys.glob(
    glue::glue("{here('./data/analyses/jvc/trapezia_cantonensis/')}/audio_chunks/*/_FastTrack/csvs/*.csv")), 
  file = map(path, read_csv, progress = FALSE, show_col_types = FALSE)) %>%
    unnest(file)

@@

# Results

## Load models

```{r}
#| label: load-models

msa_models <- dir_ls(path = here("data", "analyses", "models"), 
  regexp = ".rds$") %>% 
  as_tibble() %>% 
  transmute(path = value, 
    mod_name = str_remove(path, here("data", "analyses", "models/")), 
    mod_name = str_remove(mod_name, ".rds"), 
    model = map(path, ~ readRDS(file = .))) %>% 
  separate(mod_name, 
    into = c("word1", "word2", "mod_n", "outcome", "typicality"), 
    sep = "_", remove = F) %>% 
  unite(group, word1, word2, sep = "_") %>% 
  dplyr::select(group, mod_name:model) %>% 
  mutate(sum = map(model, clean_up)) %>% 
  suppressWarnings() 
```

## Table

```{r}
#| label: effect-table

# Simple pandoc table of the models, estimates, se, etc.
msa_models %>% 
  unnest(sum) %>% 
  dplyr::select(-model) %>% 
  knitr::kable(format = "pandoc")

## Plot

```{r}
#| label: forest-plot
#| fig.height: 8

# Simple forest plot of the estimates +/- SE
msa_models %>% 
  unnest(sum) %>% 
  mutate(typicality_lab = if_else(typicality == "cat", 
    "Typicality = categorical", "Typicality = continuous"), 
    mod_name = fct_reorder(mod_name, estimate)) %>% 
  ggplot() + 
  facet_wrap(~ typicality_lab, ncol = 1, scales = "free") + 
  aes(x = estimate, y = mod_name) + 
  geom_vline(xintercept = 0, lty = 3) + 
  geom_segment(aes(x = estimate - se, xend = estimate + se, yend = mod_name), 
    color = "#cc0033", alpha = 0.5, size = 1.5, lineend = "round") + 
  geom_point(color = "#cc0033", pch = 21, stroke = 1.5, size = 1.6) + 
  labs(y = "Model", x = "Estimate ± SE") + 
  clean_theme() + 
  theme(strip.text.x = element_text(hjust = 0))
```

>>>>

unzip(here("data", "analyses", "jvc", "anomalocaris_ornata", "MSA.zip"), exdir = here("data", "analyses", "jvc", "anomalocaris_ornata"))

@@

if(T) {
msa_raw <- tibble(
  path = Sys.glob(
    glue::glue("{here('./data/analyses/jvc/trapezia_cantonensis/')}/audio_chunks/*/_FastTrack/csvs/*.csv")), 
  file = map(path, read_csv, progress = FALSE, show_col_types = FALSE)) %>%
    unnest(file)

@@
